### 2020-12-07 README.rmd
README updated.

<!--
You can install the released version of listdown from [CRAN](https://CRAN.R-project.org) with:

@@

And the development version from [GitHub](https://github.com/) with:
-->

You can install the development version of {listdown} from [GitHub](https://github.com/) with:

>>>>

You can install the released version of listdown from [CRAN](https://CRAN.R-project.org) with:

@@

The development version of {listdown} can be installed from [GitHub](https://github.com/) with:
